Towards an Automated Sportscasting System for Chess

### 2011-05-18 paper/paper.tex
Partition based on first player's color

Unfortunately, we found that our approaches did not deliver accurate

@@

\section{Related Work}
\paragraph{Deep learning.}
\paragraph{Automated sportscasting.}
\paragraph{Automatic chess commentary.}

@@

\subsection{Sparse Autoencoding}
\subsection{Manual baseline}
As a first step towards classification, we selected chess-specific manual features from a given chess position (and a previous move):
\begin{table*}
\begin{tabular}{lp{0.6\textwidth}}
\hline
\textbf{Name} & \textbf{Description} \\ \hline
\tt{materialCount()} & \\
\tt{squareDominationCount()} & \\
\tt{isCapturing()} & \\
\tt{isEnPessant()} & \\
\tt{isLongCastle()} & \\
\tt{isCheck()} & \\
\tt{isStalemate()} & \\
\tt{isMate()} & \\
\tt{isPromotion()} & \\

\end{tabular} 
\caption{List of chess-specific manual features per position.}
\end{table*}

>>>>

Unfortunately, we found that our approaches did not deliver accurate results in our experiments. In particular, the auto-encoder's output failed to serve as a useful criterion for distinguishing between different types of themes. We examine the types of correct predictions made by our classifiers and discuss how we may improve our results in the future.

@@

\section{Related Work}
\paragraph{Deep learning.} These techniques attempt to capture complex relationships between input variables in order to transform the input into a different representation which better expresses the relevant structures that make up the input. Specifically, they compose many layers of non-linearities in order to compactly represent complex functions which can model these relationships. They have been used successfully for many different types of tasks \cite{ng-mnist,ng-vision,ng-nlp}.

\paragraph{Automated sportscasting.}

\paragraph{Automatic chess commentary.}

@@

\subsection{Sparse Autoencoding}
\subsection{Manual baseline}
As a first step towards classification, we selected chess-specific manual features from a given chess position-previousmove pair.  The position-based features involve information such as where the pieces are on the board and potential moves, while the move-based features involve binary information such as if the move is a capturing move or a check.  We list all our hand-selected manual features in Table REF.

\begin{table*}
\begin{tabular}{lp{0.6\textwidth}}
\hline
\textbf{Category} & \textbf{Description} \\ \hline
Position features & Piece location, potential moves per piece, material count, square control. \\
Move features & Capturing move, recapturing move, en passant move, long castling move, short castling move, check move, stalemate move, checkmate move, promotion move.
\end{tabular} 
\caption{List of chess-specific manual features per position.}
\end{table*}
